Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-05-05 doc/paper.tex
fix up tables

@@

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                                      & ceiling        & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU                            \\
            \hline
            Scratch                                   & 90.34          & \textbf{96.84} & 80.63          & 0              & 25.5           & 56.95          & 62.93          & 75.14          & 86.21          & 65.77          & 72.12          & 76.91          & 56.4           & 65.06                           \\
            Supervised                                & \textbf{91.81} & 96.74          & \textbf{84.11} & \textbf{0.21}  & \textbf{34.68} & \textbf{57.64} & \textbf{81.53} & \textbf{77.63} & \textbf{89.82} & \textbf{85.76} & \textbf{76.03} & \textbf{79.27} & \textbf{57.67} & \textbf{70.22} \textbf{(+5.16)} \\
            \hline
            PointContrast                             & 91.97          & \textbf{96.67} & 82.4           & 0              & 17.84          & 56.49          & \textbf{75.39} & \textbf{77.63} & 87.35          & 63.3           & 73.53          & \textbf{79.55} & 58.76          & 66.22 \textbf{(+1.16)}          \\
            PointContrast - Same Scan                 & 91.03          & 96.27          & \textbf{82.8}  & 0              & 31.53          & 57.27          & 69.33          & 76.97          & \textbf{88.83} & 45.49          & 71.02          & 77.09          & 57.06          & 64.97 (-0.09)                   \\
            PointContrast - 70\% overlap              & 91.85          & 96.56          & 83.55          & 0              & 28.25          & 59.36          & 73.53          & 78.51          & 88.28          & 79.95          & 74.61          & 76             & 61.08          & 68.58 \textbf{(+3.52)}          \\
            Contrastive Scene Contexts                & \textbf{92.34} & 96.02          & 83.53          & 0              & \textbf{40.88} & \textbf{57.73} & 72.11          & 77.5           & 88.15          & \textbf{74.61} & \textbf{74.52} & 76.45          & \textbf{62.64} & 68.96 \textbf{(+3.9)}           \\
            Contrastive Scene Contexts - Same Scan    & 91.68          & 96.59          & 83.21          & 0              & 40.38          & 58.12          & 70.42          & 76.77          & 87.13          & 69.33          & 68.77          & 82.34          & 58.45          & 67.94 \textbf{(+2.88)}          \\
            Contrastive Scene Contexts - 70\% overlap & 92.68          & 96.63          & 83.99          & 0              & 42.37          & 55.95          & 77.17          & 75.74          & 89.57          & 82.74          & 73.45          & 80.67          & 60.55          & \textbf{70.12} \textbf{(+5.06)} \\
            DepthContrast                             & 90.99          & 95.45          & 80.99          & 0              & 32.52          & 51.94          & 61.57          & 74.55          & 87.28          & 71.62          & 71.34          & 67.71          & 57.85          & 64.91 (-0.15)                   \\
            CME \textbf{(Ours)}                       & 90.8           & 96.57          & 82.52          & \textbf{0.110} & 30.94          & 56.94          & 68.71          & 75.12          & 88.48          & 71.7           & 72.17          & 73.783         & 56.35          & 66.48 \textbf{(+1.42)}          \\
        \end{tabular}
    }
    \caption{S3DIS Semantic Segmentation results (mIOU)}
    \label{table:s3disResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c | c }
                                                      & beam & column        & window        & door & table         & chair         & sofa          & bookcase      & board         & clutter       & mAP@0.5                       \\
            \hline
            Scratch                                   & 0    & 12.8          & 61.7          & 92.0 & 51.4          & 87.3          & 62.4          & 38.5          & 87.0          & 37.1          & 53.0                          \\
            Supervised                                & 0    & 26.0          & 74.3          & 84.5 & 43.3          & 87.3          & \textbf{81.8} & 37.4          & \textbf{85.4} & \textbf{41.2} & \textbf{56.2} (+3.2)          \\
            \hline
            PointContrast                             & 0    & 24.7          & 67.9          & 90.7 & 43.8          & 92.0          & 72.7          & 32.3          & 85.6          & 38.0          & 54.8 \textbf{(+1.8)}          \\
            PointContrast - Same Scan                 & 0    & 19.8          & 70.7          & 92.1 & 48.4          & 90.5          & 81.8          & 38.4          & 90.4          & 34.1          & 56.6 \textbf{(+3.6)}          \\
            PointContrast - 70\% overlap              & 0    & 22.6          & 71.6          & 94.6 & 45.8          & 87.9          & 71.7          & 37.0          & 81.0          & 40.9          & 55.3 \textbf{(+2.3)}          \\
            Contrastive Scene Contexts                & 0    & 32.9          & 69.2          & 93.0 & 47.6          & 87.5          & 80.9          & 39.6          & 87.5          & 40.4          & 57.8 \textbf{(+4.8)}          \\
            Contrastive Scene Contexts - Same Scan    & 0    & 32.0          & 69.3          & 96.1 & 38.7          & 89.4          & 87.6          & 38.8          & 81.3          & 38.8          & 57.2 \textbf{(+4.2)}          \\
            Contrastive Scene Contexts - 70\% overlap & 0    & 27.2          & 76.9          & 95.4 & 42.2          & 90.3          & 90.9          & 42.6          & 84.7          & 38.7          & \textbf{58.9} \textbf{(+5.9)} \\
            DepthContrast                             & 0    & 40.3          & 68.4          & 74.9 & 42.2          & 87.8          & 62.4          & 33.3          & 78.1          & 35.5          & 52.3 (-0.7)                   \\
            CME \textbf{(Ours)}                       & 0    & \textbf{35.0} & \textbf{70.0} & 83.4 & \textbf{53.9} & \textbf{88.9} & 71.7          & \textbf{42.2} & 76.1          & 36.7          & 55.8 \textbf{(+2.8)}          \\
        \end{tabular}
    }
    \caption{S3DIS Instance Segmentation Results (mAP@0.5)}
    \label{table:s3disInstanceSegmention}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                                      & 5\%                    & 10\%                   & 20\%                   & 30\%                   & 40\%                   & 100\%                  \\
            \hline
            Scratch                                   & 42.2                   & 51.09                  & 58.23                  & 59.23                  & 62.17                  & 67.43                  \\
            \hline
            PointContrast                             & 44.79 \textbf{(+2.59)} & 55.28 \textbf{(+4.19)} & 57.98 (-0.25)          & 58.97 (-0.26)          & 63.17 \textbf{(+1.00)} & 66.88 (-0.55)          \\
            Contrastive Scene Contexts                & 42.6 \textbf{(+0.4)}   & 53.03 \textbf{(+1.94)} & 57.28 (-0.95)          & 62.15 \textbf{(+2.92)} & 65.15 \textbf{(+2.98)} & 67.62 \textbf{(+0.19)} \\
            Contrastive Scene Contexts - 70\% overlap & 45.44 \textbf{(+3.24)} & 50.84 (-0.25)          & 59.26 \textbf{(+1.03)} & 59.72 \textbf{(+0.49)} & 62.72 \textbf{(+0.55)} & 68.01 \textbf{(+0.58)} \\
            Contrastive Scene Contexts - same scan    & 44.09 \textbf{(+1.89)} & 50.88 (-0.21)          & 56.64 (-1.59)          & 58.9 (-0.33)           & 61.50 (-0.67)          & 67.37 (-0.06)          \\
            CME \textbf{(Ours)}                       & 44.04 \textbf{(+1.84)} & 52.97 \textbf{(+1.88)} & 58.6 \textbf{(+0.37)}  & 60.73 \textbf{(+1.5)}  & 63.31 \textbf{(+1.14)} & 67.71 \textbf{(+0.28)} \\
        \end{tabular}
    }
    \caption{Scannet Semantic Segmentation with Partial Data  (mIOU)}
    \label{table:scannetVaryingDataAmount}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.7\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                       & 5\%                  & 10\%          & 20\%                 & 30\%                 & 40\%        & 100\%                \\
            \hline
            Scratch                    & 26.9                 & \textbf{31.1} & 40.7                 & 42.2                 & 45.7        & 49.0                 \\
            \hline
            PointContrast              & 27.0 \textbf{(+0.1)} & 35.3          & 40.5 (-0.2)          & 43.0 \textbf{(+0.8)} & 43.9 (-1.8) & 49.1 \textbf{(+0.1)} \\
            Contrastive Scene Contexts & 29.8 \textbf{(+2.9)} & 35.5          & 41.6 \textbf{(+0.9)} & 42.9 \textbf{(+0.7)} & 44.6 (-1.1) & 49.3 \textbf{(+0.3)} \\
            CME \textbf{(Ours)}        & 25.5 (-1.4)          & 35.5          & 39.1 (-1.6)          & 42.4 \textbf{(+0.2)} & 43.6 (-2.1) & 48.5 (-0.5)          \\
        \end{tabular}
    }
    \caption{Scannet Instance Segmentation with Partial Data  (mAP@0.5)}
    \label{table:scannetInstanceVaryingDataAmount}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.7\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c }
                                       & 5\%                    & 10\%                   & 20\%                   & 30\%                   & 40\%                   & 100\%                  \\
            \hline
            Scratch                    & 39.2                   & 40.43                  & 41.06                  & 41.67                  & 40.79                  & 41.01                  \\
            \hline
            PointContrast              & 40.29 \textbf{(1.09)}  & 42.59 \textbf{(+2.16)} & 42.2  \textbf{(+1.14)} & 41.65 (-0.02)          & 42.99 \textbf{(+2.2)}  & 42.09 \textbf{(+1.08)} \\
            Contrastive Scene Contexts & 40.6 \textbf{(+1.4)}   & 42.21 \textbf{(+1.78)} & 42.26 \textbf{(+1.2)}  & 42.24 \textbf{(+0.57)} & 44.29 \textbf{(+3.5)}  & 43.01 \textbf{(+2.0)}  \\
            CME \textbf{(Ours)}        & 39.49 \textbf{(+0.29)} & 40.90 \textbf{(+0.47)} & 40.91 (-0.15)          & 41.82 \textbf{(+0.15)} & 41.77 \textbf{(+0.98)} & 42.04 \textbf{(+1.03)} \\
        \end{tabular}
    }
    \caption{KITTI Semantic Segmentation results (mIOU)}
    \label{table:kittiSemanticResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.4\textwidth}{!}{
        \begin{tabular}{c | c c c}
                                       & Scannet              & SunRGBD              \\
            \hline
            Scratch                    & 35.2                 & 32.0                 \\
            \hline
            PointContrast              & 36.7 \textbf{(+1.5)} & 34.2 \textbf{(+2.2)} \\
            Contrastive Scene Contexts & 36.1 \textbf{(+0.9)} & 35.1 \textbf{(+3.1)} \\
            DepthContrast              & 33.9 (-1.3)          &                      \\
            CME \textbf{(Ours)}        & 37.7 \textbf{(+2.5)} & 33.1 \textbf{(+1.1)} \\
        \end{tabular}
    }
    \caption{Object Detection using VoteNet  (mAP)}
    \label{table:scannetObjectDetection}
\end{table*}

>>>>

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c | c c c c c c | c c c c c c |}
                                &      &          & \multicolumn{6}{|c|}{Semantic Segmentation (mIOU)} & \multicolumn{6}{|c|}{Instance Segmentation (mAP@0.5)}                                                                                                                                                                                                                        \\
                                & Scan & Overlap  & 5\%                                                & 10\%                                                  & 20\%                 & 30\%                 & 40\%                 & 100\%                 & 5\%                  & 10\%          & 20\%                 & 30\%                 & 40\%        & 100\%                \\
            \hline
            Scratch             & --   & --       & 42.2                                               & 51.1                                                  & 58.2                 & 59.2                 & 62.2                 & 67.4                  & 26.9                 & \textbf{31.1} & 40.7                 & 42.2                 & 45.7        & 49.0                 \\
            \hline
            PointContrast       & Pair & $>$ 30\% & 44.8 \textbf{(+2.6)}                               & 55.3 \textbf{(+4.2)}                                  & 58.0 (-0.2)          & 59.0 (-0.2)          & 63.2 \textbf{(+1.0)} & 66.9 (-0.5)           & 27.0 \textbf{(+0.1)} & 35.3          & 40.5 (-0.2)          & 43.0 \textbf{(+0.8)} & 43.9 (-1.8) & 49.1 \textbf{(+0.1)} \\
            PointContrast       & Pair & $>$ 70\% & 46.1 \textbf{(+3.9)}                               & 50.7 (-0.4)                                           & 58.0 (-0.2)          & 61.9 \textbf{(+2.7)} & 62.6 \textbf{(+0.4)} & 67.3 (-0.1)           & --                   & --            & --                   & --                   & --          & --                   \\
            PointContrast       & Same & --       & 45.5 \textbf{(+3.3)}                               & 48.8 (-2.3)                                           & 56.7 (-1.5)          & 59.3 \textbf{(+0.1)} & 61.7 (-0.5)          & 66.5 (-0.9)           & --                   & --            & --                   & --                   & --          & --                   \\
            CSC                 & Pair & $>$ 30\% & 42.6 \textbf{(+0.4)}                               & 53.0 \textbf{(+1.9)}                                  & 57.3 (-0.9)          & 62.2 \textbf{(+3.0)} & 65.2 \textbf{(+3.0)} & 67.6 \textbf{(+0.2)}  & 29.8 \textbf{(+2.9)} & 35.5          & 41.6 \textbf{(+0.9)} & 42.9 \textbf{(+0.7)} & 44.6 (-1.1) & 49.3 \textbf{(+0.3)} \\
            CSC                 & Pair & $>$ 70\% & 45.4 \textbf{(+3.2)}                               & 50.8 (-0.3)                                           & 59.3 \textbf{(+1.1)} & 59.7 \textbf{(+0.5)} & 62.7 \textbf{(+0.5)} & 68.0 \textbf{(+0.6)}  & --                   & --            & --                   & --                   & --          & --                   \\
            CSC                 & Same & --       & 44.1 \textbf{(+1.9)}                               & 50.9 (-0.2)                                           & 56.6 (-1.6)          & 58.9 (-0.3)          & 61.5 (-0.7)          & 67.4 \textbf{(+0.0)}  & --                   & --            & --                   & --                   & --          & --                   \\
            DepthContrast       & Same & --       & 49.3 \textbf{(+7.1)}                               & 54.3 \textbf{(+3.2)}                                  & 58.2 \textbf{(+0.0)} & --                   & --                   & --                    & 24.9 (-2.0)          & 33.8          & 38.2 (-2.5)          & --                   & --          & --                   \\
            CME \textbf{(Ours)} & Same & --       & 44.0 \textbf{(+1.8)}                               & 53.0 \textbf{(+1.9)}                                  & 58.6 \textbf{(+0.4)} & 60.7 \textbf{(+1.5)} & 63.3 \textbf{(+1.1)} & 67.7 \textbf{(+0.28)} & 25.5 (-1.4)          & 35.5          & 39.1 (-1.6)          & 42.4 \textbf{(+0.2)} & 43.6 (-2.1) & 48.5 (-0.5)          \\
        \end{tabular}
    }
    \caption{Scannet downstream semantic (mIOU) and instance (mAP@0.5) segmentation performance using weights pre-trained in Scannet}
    \label{table:scannetVaryingDataAmount}
\end{table*}

\begin{table}
    \centering
    \resizebox{0.45\textwidth}{!}{
        \begin{tabular}{ c | c c c c }
                                & Scan & Overlap  & Semantic (mIOU)               & Instance (mAP@0.5)            \\
            \hline
            Scratch             & --   & --       & 65.1                          & 53.0                          \\
            Supervised          & --   & --       & \textbf{70.2} \textbf{(+5.1)} & \textbf{56.2} \textbf{(+3.2)} \\
            \hline
            PointContrast       & Pair & $>$ 30\% & 66.2 \textbf{(+1.1)}          & 54.8 \textbf{(+1.8)}          \\
            PointContrast       & Pair & $>$ 70\% & 68.6 \textbf{(+3.5)}          & 55.3 \textbf{(+2.3)}          \\
            PointContrast       & Same & --       & 65.0 (-0.1)                   & 56.6 \textbf{(+3.6)}          \\
            CSC                 & Pair & $>$ 30\% & 69.0 \textbf{(+3.9)}          & 57.8 \textbf{(+4.8)}          \\
            CSC                 & Pair & $>$ 70\% & \textbf{70.1} \textbf{(+5.0)} & \textbf{58.9} \textbf{(+5.9)} \\
            CSC                 & Same & --       & 67.9 \textbf{(+2.8)}          & 57.2 \textbf{(+4.2)}          \\
            DepthContrast       & Same & --       & 64.9 (-0.2)                   & 52.3 (-0.7)                   \\
            CME \textbf{(Ours)} & Same & --       & 66.5 \textbf{(+1.4)}          & 55.8 \textbf{(+2.8)}          \\
        \end{tabular}
    }
    \caption{S3DIS downstream semantic (mIOU) and instance (mAP@0.5) segmentation performance using weights pre-trained in Scannet}
    \label{table:s3disResults}
\end{table}

\begin{table}
    \centering
    \resizebox{0.5\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c }
                                & 5\%                  & 10\%                 & 20\%                  & 30\%                 & 40\%                 & 100\%                \\
            \hline
            Scratch             & 39.2                 & 40.4                 & 41.1                  & 41.7                 & 40.8                 & 41.0                 \\
            \hline
            PointContrast       & 40.3 \textbf{(1.1)}  & 42.6 \textbf{(+2.2)} & 42.2  \textbf{(+1.1)} & 41.7 \textbf{(+0.0)} & 43.0 \textbf{(+2.2)} & 42.1 \textbf{(+1.1)} \\
            CSC                 & 40.6 \textbf{(+1.4)} & 42.2 \textbf{(+1.8)} & 42.3 \textbf{(+1.2)}  & 42.2 \textbf{(+0.6)} & 44.3 \textbf{(+3.5)} & 43.0 \textbf{(+2.0)} \\
            DepthContrast       & 39.7 \textbf{(+0.5)} & 40.9 \textbf{(+0.5)} & --                    & --                   & --                   & --                   \\
            CME \textbf{(Ours)} & 39.5 \textbf{(+0.3)} & 40.9 \textbf{(+0.5)} & 40.9 (-0.2)           & 41.8 \textbf{(+0.1)} & 41.8 \textbf{(+1.0)} & 42.0 \textbf{(+1.0)} \\
        \end{tabular}
    }
    \caption{KITTI Semantic Segmentation results (mIOU)}
    \label{table:kittiSemanticResults}
\end{table}

\begin{table}
    \centering
    \resizebox{0.3\textwidth}{!}{
        \begin{tabular}{c | c c c}
                                       & Scannet              & SunRGBD              \\
            \hline
            Scratch                    & 35.2                 & 32.0                 \\
            \hline
            PointContrast              & 36.7 \textbf{(+1.5)} & 34.2 \textbf{(+2.2)} \\
            Contrastive Scene Contexts & 36.1 \textbf{(+0.9)} & 35.1 \textbf{(+3.1)} \\
            DepthContrast              & 33.9 (-1.3)          & 32.9 \textbf{(+0.9)} \\
            CME \textbf{(Ours)}        & 37.7 \textbf{(+2.5)} & 33.1 \textbf{(+1.1)} \\
        \end{tabular}
    }
    \caption{Object Detection using VoteNet  (mAP)}
    \label{table:scannetObjectDetection}
\end{table}

@@

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                                      & ceiling        & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU                            \\
            \hline
            Scratch                                   & 90.34          & \textbf{96.84} & 80.63          & 0              & 25.5           & 56.95          & 62.93          & 75.14          & 86.21          & 65.77          & 72.12          & 76.91          & 56.4           & 65.06                           \\
            Supervised                                & \textbf{91.81} & 96.74          & \textbf{84.11} & \textbf{0.21}  & \textbf{34.68} & \textbf{57.64} & \textbf{81.53} & \textbf{77.63} & \textbf{89.82} & \textbf{85.76} & \textbf{76.03} & \textbf{79.27} & \textbf{57.67} & \textbf{70.22} \textbf{(+5.16)} \\
            \hline
            PointContrast                             & 91.97          & \textbf{96.67} & 82.4           & 0              & 17.84          & 56.49          & \textbf{75.39} & \textbf{77.63} & 87.35          & 63.3           & 73.53          & \textbf{79.55} & 58.76          & 66.22 \textbf{(+1.16)}          \\
            PointContrast - Same Scan                 & 91.03          & 96.27          & \textbf{82.8}  & 0              & 31.53          & 57.27          & 69.33          & 76.97          & \textbf{88.83} & 45.49          & 71.02          & 77.09          & 57.06          & 64.97 (-0.09)                   \\
            PointContrast - 70\% overlap              & 91.85          & 96.56          & 83.55          & 0              & 28.25          & 59.36          & 73.53          & 78.51          & 88.28          & 79.95          & 74.61          & 76             & 61.08          & 68.58 \textbf{(+3.52)}          \\
            Contrastive Scene Contexts                & \textbf{92.34} & 96.02          & 83.53          & 0              & \textbf{40.88} & \textbf{57.73} & 72.11          & 77.5           & 88.15          & \textbf{74.61} & \textbf{74.52} & 76.45          & \textbf{62.64} & 68.96 \textbf{(+3.9)}           \\
            Contrastive Scene Contexts - Same Scan    & 91.68          & 96.59          & 83.21          & 0              & 40.38          & 58.12          & 70.42          & 76.77          & 87.13          & 69.33          & 68.77          & 82.34          & 58.45          & 67.94 \textbf{(+2.88)}          \\
            Contrastive Scene Contexts - 70\% overlap & 92.68          & 96.63          & 83.99          & 0              & 42.37          & 55.95          & 77.17          & 75.74          & 89.57          & 82.74          & 73.45          & 80.67          & 60.55          & \textbf{70.12} \textbf{(+5.06)} \\
            DepthContrast                             & 90.99          & 95.45          & 80.99          & 0              & 32.52          & 51.94          & 61.57          & 74.55          & 87.28          & 71.62          & 71.34          & 67.71          & 57.85          & 64.91 (-0.15)                   \\
            CME \textbf{(Ours)}                       & 90.8           & 96.57          & 82.52          & \textbf{0.110} & 30.94          & 56.94          & 68.71          & 75.12          & 88.48          & 71.7           & 72.17          & 73.783         & 56.35          & 66.48 \textbf{(+1.42)}          \\
        \end{tabular}
    }
    \caption{S3DIS Semantic Segmentation results (mIOU)}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c | c }
                                                      & beam & column        & window        & door & table         & chair         & sofa          & bookcase      & board         & clutter       & mAP@0.5                       \\
            \hline
            Scratch                                   & 0    & 12.8          & 61.7          & 92.0 & 51.4          & 87.3          & 62.4          & 38.5          & 87.0          & 37.1          & 53.0                          \\
            Supervised                                & 0    & 26.0          & 74.3          & 84.5 & 43.3          & 87.3          & \textbf{81.8} & 37.4          & \textbf{85.4} & \textbf{41.2} & \textbf{56.2} (+3.2)          \\
            \hline
            PointContrast                             & 0    & 24.7          & 67.9          & 90.7 & 43.8          & 92.0          & 72.7          & 32.3          & 85.6          & 38.0          & 54.8 \textbf{(+1.8)}          \\
            PointContrast - Same Scan                 & 0    & 19.8          & 70.7          & 92.1 & 48.4          & 90.5          & 81.8          & 38.4          & 90.4          & 34.1          & 56.6 \textbf{(+3.6)}          \\
            PointContrast - 70\% overlap              & 0    & 22.6          & 71.6          & 94.6 & 45.8          & 87.9          & 71.7          & 37.0          & 81.0          & 40.9          & 55.3 \textbf{(+2.3)}          \\
            Contrastive Scene Contexts                & 0    & 32.9          & 69.2          & 93.0 & 47.6          & 87.5          & 80.9          & 39.6          & 87.5          & 40.4          & 57.8 \textbf{(+4.8)}          \\
            Contrastive Scene Contexts - Same Scan    & 0    & 32.0          & 69.3          & 96.1 & 38.7          & 89.4          & 87.6          & 38.8          & 81.3          & 38.8          & 57.2 \textbf{(+4.2)}          \\
            Contrastive Scene Contexts - 70\% overlap & 0    & 27.2          & 76.9          & 95.4 & 42.2          & 90.3          & 90.9          & 42.6          & 84.7          & 38.7          & \textbf{58.9} \textbf{(+5.9)} \\
            DepthContrast                             & 0    & 40.3          & 68.4          & 74.9 & 42.2          & 87.8          & 62.4          & 33.3          & 78.1          & 35.5          & 52.3 (-0.7)                   \\
            CME \textbf{(Ours)}                       & 0    & \textbf{35.0} & \textbf{70.0} & 83.4 & \textbf{53.9} & \textbf{88.9} & 71.7          & \textbf{42.2} & 76.1          & 36.7          & 55.8 \textbf{(+2.8)}          \\
        \end{tabular}
    }
    \caption{S3DIS Instance Segmentation Results (mAP@0.5)}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                                      & 5\%                    & 10\%                   & 20\%                   & 30\%                   & 40\%                   & 100\%                  \\
            \hline
            Scratch                                   & 42.2                   & 51.09                  & 58.23                  & 59.23                  & 62.17                  & 67.43                  \\
            \hline
            PointContrast                             & 44.79 \textbf{(+2.59)} & 55.28 \textbf{(+4.19)} & 57.98 (-0.25)          & 58.97 (-0.26)          & 63.17 \textbf{(+1.00)} & 66.88 (-0.55)          \\
            Contrastive Scene Contexts                & 42.6 \textbf{(+0.4)}   & 53.03 \textbf{(+1.94)} & 57.28 (-0.95)          & 62.15 \textbf{(+2.92)} & 65.15 \textbf{(+2.98)} & 67.62 \textbf{(+0.19)} \\
            Contrastive Scene Contexts - 70\% overlap & 45.44 \textbf{(+3.24)} & 50.84 (-0.25)          & 59.26 \textbf{(+1.03)} & 59.72 \textbf{(+0.49)} & 62.72 \textbf{(+0.55)} & 68.01 \textbf{(+0.58)} \\
            Contrastive Scene Contexts - same scan    & 44.09 \textbf{(+1.89)} & 50.88 (-0.21)          & 56.64 (-1.59)          & 58.9 (-0.33)           & 61.50 (-0.67)          & 67.37 (-0.06)          \\
            CME \textbf{(Ours)}                       & 44.04 \textbf{(+1.84)} & 52.97 \textbf{(+1.88)} & 58.6 \textbf{(+0.37)}  & 60.73 \textbf{(+1.5)}  & 63.31 \textbf{(+1.14)} & 67.71 \textbf{(+0.28)} \\
        \end{tabular}
    }
    \caption{Scannet Semantic Segmentation with Partial Data  (mIOU)}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.7\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                       & 5\%                  & 10\%          & 20\%                 & 30\%                 & 40\%        & 100\%                \\
            \hline
            Scratch                    & 26.9                 & \textbf{31.1} & 40.7                 & 42.2                 & 45.7        & 49.0                 \\
            \hline
            PointContrast              & 27.0 \textbf{(+0.1)} & 35.3          & 40.5 (-0.2)          & 43.0 \textbf{(+0.8)} & 43.9 (-1.8) & 49.1 \textbf{(+0.1)} \\
            Contrastive Scene Contexts & 29.8 \textbf{(+2.9)} & 35.5          & 41.6 \textbf{(+0.9)} & 42.9 \textbf{(+0.7)} & 44.6 (-1.1) & 49.3 \textbf{(+0.3)} \\
            CME \textbf{(Ours)}        & 25.5 (-1.4)          & 35.5          & 39.1 (-1.6)          & 42.4 \textbf{(+0.2)} & 43.6 (-2.1) & 48.5 (-0.5)          \\
        \end{tabular}
    }
    \caption{Scannet Instance Segmentation with Partial Data  (mAP@0.5)}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.7\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c }
                                       & 5\%                    & 10\%                   & 20\%                   & 30\%                   & 40\%                   & 100\%                  \\
            \hline
            Scratch                    & 39.2                   & 40.43                  & 41.06                  & 41.67                  & 40.79                  & 41.01                  \\
            \hline
            PointContrast              & 40.29 \textbf{(1.09)}  & 42.59 \textbf{(+2.16)} & 42.2  \textbf{(+1.14)} & 41.65 (-0.02)          & 42.99 \textbf{(+2.2)}  & 42.09 \textbf{(+1.08)} \\
            Contrastive Scene Contexts & 40.6 \textbf{(+1.4)}   & 42.21 \textbf{(+1.78)} & 42.26 \textbf{(+1.2)}  & 42.24 \textbf{(+0.57)} & 44.29 \textbf{(+3.5)}  & 43.01 \textbf{(+2.0)}  \\
            CME \textbf{(Ours)}        & 39.49 \textbf{(+0.29)} & 40.90 \textbf{(+0.47)} & 40.91 (-0.15)          & 41.82 \textbf{(+0.15)} & 41.77 \textbf{(+0.98)} & 42.04 \textbf{(+1.03)} \\
        \end{tabular}
    }
    \caption{KITTI Semantic Segmentation results (mIOU)}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.4\textwidth}{!}{
        \begin{tabular}{c | c c c}
                                       & Scannet              & SunRGBD              \\
            \hline
            Scratch                    & 35.2                 & 32.0                 \\
            \hline
            PointContrast              & 36.7 \textbf{(+1.5)} & 34.2 \textbf{(+2.2)} \\
            Contrastive Scene Contexts & 36.1 \textbf{(+0.9)} & 35.1 \textbf{(+3.1)} \\
            DepthContrast              & 33.9 (-1.3)          &                      \\
            CME \textbf{(Ours)}        & 37.7 \textbf{(+2.5)} & 33.1 \textbf{(+1.1)} \\
        \end{tabular}
    }
    \caption{Object Detection using VoteNet  (mAP)}
\end{table*}
